\fontsize{10.5pt}{10.5pt}\selectfont
\begin{thebibliography}{10}

\bibitem{paper:Google-MapReduce}
Jeffrey Dean and Sanjay Ghemawat.
\newblock MapReduce: Simplified Data Processing on Large Clusters.
\newblock In OSDI, 2004

\bibitem{site:Hadoop}
Hadoop Project.
\newblock http://hadoop.apache.org/

\bibitem{site:Yahoo}
Yahoo! Launches World’s Largest Hadoop Production Application, Yahoo! Developer Network.
\newblock http://developer.yahoo.com/blogs/hadoop/2008/02/yahoo-worldslargest-production-hadoop.html


\bibitem{paper:Hadoop-Performance-in-Heterogeneous}
Matei Zaharia, Andy Konwinski, Anthony D. Joseph, Randy Katz, Ion Stoica.
\newblock Improving MapReduce Performance in HeterogeneousEnvironments.
\newblock IN OSDI, 2008.8


\bibitem{book:Hadoop}
Tom White.
\newblock Hadoop: The Definitive Guide.
\newblock Yahoo Press; Second Edition edition (October 12, 2010)

\bibitem{site:hdfs}
Hadoop Distributed File System.
\newblock http://hadoop.apache.org/hdfs/

\bibitem{site:hadoop-counter}
MapReduce:默认Counter的含义.
\newblock http://langyu.iteye.com/blog/1171091

\bibitem{site:weblog}
WEB日志格式.
\newblock http://webdataanalysis.net/reference-and-source/weblog-format/

\bibitem{site:nginx}
Nginx.
\newblock http://www.nginx.org/

\bibitem{site:netcraft_nginx}
May 2012 Web Server Survey.
\newblock http://news.netcraft.com/archives/2012/05/02/may-2012-web-server-survey.html


\bibitem{paper:A-Dynamic-MapReduce-Scheduler-for-Heterogeneous-Workloads}
Chao Tian, Haojie Zhou,Yongqiang He, Li Zha.
\newblock A Dynamic MapReduce Scheduler for Heterogeneous Workloads
\newblock in Proceedings of the 2009 Eighth International Conference on Grid and Cooperative Computing, ser. GCC ’09. Washington, DC, USA: IEEE Computer Society, 2009, pp.218–224

% other

\bibitem{paper:Apache-Hadoop-Performance-Tuning-Methodologies-and-Best-Practices}
Shrinivas B. Joshi.
\newblock Apache Hadoop Performance-Tuning Methodologies and Best Practices
\newblock in Proceedings of the 2009 Eighth International Conference on Grid and Cooperative Computing, ser. GCC ’09. Washington, DC, USA: IEEE Computer Society, 2009, pp.241-242 

\bibitem{site:hadoop-wiki}
Hadoop Wiki.
\newblock http://wiki.apache.org/hadoop/

\bibitem{book:java}
Bruce Eckel、陈昊鹏.
\newblock Java编程思想(第4版).
\newblock 机械工业出版社

\bibitem{book:python}
Magnus Lie Hetland、司维等.
\newblock Python基础教程(第2版).
\newblock 人民邮电出版社

\bibitem{book:linux}
鸟哥、王世江.
\newblock 鸟哥的Linux私房菜:基础学习篇(第三版).
\newblock 人民邮电出版社

\end{thebibliography}
